Gap Puzzles

### 2020-01-05 gap/article/llncs2e/article.tex
report

\subsection{Search Strategy}
\paragraph{}
Initially, we opted to use an ordering function to order the coordinates. This way, we would only get one solution and not
permutations of the same solution. Later, while doing timed tests, we noticed irregularities. To combat these, we found
a new way to search solutions, a random function. After adding this function to our project and removing the precious
ordering one, we noticed great improvement in our tests.

\begin{figure}
    \begin{center}
        \includegraphics[scale=0.4]{images/random.png}
        \caption{Random selection predicate} \label{fig4}
    \end{center}
\end{figure}

@@

\paragraph{}
This irregular behaviour told us the solution was imperfect somewhere. With that knowledge, we felt incentivized to search new ways of labeling variables.
We then found we could add a random function to the labeling and once we implemented it, it showed incredible results.

\begin{figure}
    \begin{center}
        \includegraphics[scale=0.6]{images/graph2.png}
        \caption{Times graph after random labeling} \label{fig5}
    \end{center}
\end{figure}

>>>>

\subsection{Search Strategy}
\paragraph{}
For labeling we made an ordering function in \textbf{crescent\_order(+B)} predicate. This predicate orders the coordinates of the points
top-down and left-right, improving the labeling times for smaller boards.

\begin{figure}
    \begin{center}
        \includegraphics[scale=0.5]{images/crescent.png}
        \caption{Crescent ordering} \label{fig4}
    \end{center}
\end{figure}

\paragraph{}
For bigger boards, \textbf{crescent\_order(+B)} predicate is an expensive task, as it runs through the whole list of points to apply the restrictions.
For this reason, if the board is of order 15 or bigger, this predicate is not used.
\paragraph{}
We also added a random function that was given in the classes. This function allows \textbf{labeling} predicate to select the value in a random way.

\begin{figure}
    \begin{center}
        \includegraphics[scale=0.5]{images/random.png}
        \caption{Random selection predicate} \label{fig4}
    \end{center}
\end{figure}

@@

\paragraph{}
This irregular behaviour told us the solution was imperfect somewhere. With that knowledge, we felt incentivized to search new ways of labeling variables.
We then found we could add a random function to the labeling and once we implemented it, it showed incredible results. After more testing, we reached the conclusion
that the best way to search for solutions in smaller boards was to use \textbf{crescent\_order(+B)}, but to bigger boards it was a waste of time. With this in mind,
we added a condition where if the board was of order 14 or below, it would use \textbf{crescent\_order(+B)}.

\begin{figure}
    \begin{center}
        \includegraphics[scale=0.5]{images/graph2.png}
        \caption{Times graph after random labeling} \label{fig5}
    \end{center}
\end{figure}
